---
title: "Exercise-6"
author: "Alexandra Anderson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
packages_needed <- c("ggplot2", # graphics
                     "dplyr",
                     "arm", # display() etc.
                     "MASS",
                     "ggfortify",
                     "nlme",
                     "lme4",
                     "lmerTest",
                     "emmeans",
                     "ggtext",
                     "patchwork"
                     )
pk_to_install <- packages_needed [!( packages_needed %in% rownames(installed.packages())  )]
if(length(pk_to_install)>0 ){
  install.packages(pk_to_install,repos="http://cran.r-project.org")
}
#lapply(packages_needed, require, character.only = TRUE)
library(ggplot2)
library(dplyr)
library(arm)
library(MASS)
library(ggfortify)
library(nlme)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggtext)
library(patchwork)
```

## R Markdown

[Journal Article Link](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0186525)

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

## Including Plots

You can also embed plots, for example:

```{r new upload}
bat<- read.csv("TC_Data.csv")
bat$TotLatL<-as.numeric(bat$TotLatL)
bat<-na.omit(bat) 
```

```{r model}
lmeModel <- lmer(TotLatL ~ Treatment*bat + (1|bat), data=bat)
anova(lmeModel)
```

```{r model summary}
summary(lmeModel)
```

```{r check model, fig.width=9.5, fig.height=9}
performance::check_model(lmeModel)
```

```{r emmeans}
#calculate model-adjusted means (e.g. estimated marginal means)
bat_emm <- emmeans(lmeModel, "bat", "Treatment")
bat_emm
```

```{r Summary}
summary <- bat %>%
  group_by(bat, TotLatL) %>%
  summarise(n = n(),
           mean_TotLatL=mean(TotLatL),
           se_TotLatL=sd(TotLatL)/sqrt(n()))
            
summary
```

```{r emmeans as dataframe}
data_emm <- as.data.frame(summary(bat_emm))

data_emm
#model-adjusted means (emm) are identical to raw means (see above) since nothing really being adjusted in fully balanced experiment.
```

```{r}
p<- ggplot(data_emm, aes(x=Treatment, y=emmean, group=bat, color=bat)) + 
  geom_line() +
  geom_point(size=4)+
  geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), width=.2)+
  labs(title="Distance Traveled Per Season (marginal means +/- 1 SE)", x="Season", y = "Distance Traveled (miles)")
p
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
